---
title: "rDEA"
author: "Alex Bender"
date: "May 17, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
#install.packages("rDEA")
#install.packages("deaR")
library(rDEA)
library(deaR)
```

First, let's load the station data using RStudio's read.csv function. 
```{r}
#load and explore the structure of the data
station_df <- read.csv("StationEfficiency.csv")
str(station_df)
```
```{r}
#station_df$Station <- factor(station_df$Station, levels = station_df$Station[order(station_df$Status)])

#make list of labels for efficiency
x <- c("Always Efficient", "Depends", "Always Not Efficient")

station_df %>%
  mutate(Status =  factor(Status, levels = x)) %>%  #label stations by efficiency
  arrange(Status) %>% #arrange in order
  arrange(Station)-> station_df

```


Now let's load the Input & Output data in order to run DEA and find cross-efficiencies. 

```{r}
#load data
d<-read.csv("DEA_inputs_outputs_Malak2.csv", header=TRUE) %>% as.data.frame()

#create dea data object with selected inputs and outputs - Model 1
dea_data <- read_data(d, dmus = 1, inputs = c("Station_Flow_Rank","Test_Scores","Staff..","Station_Duration"), outputs = c("IRF_forms","IRF_Com","VIF_forms","VIF_Com"))

#create dea data object with selected inputs and outputs - Model 2
dea_data2 <- read_data(d, dmus = 1, inputs = c("Station_Flow_Rank","Test_Scores","Staff..","Station_Duration"), outputs = c("IRF_forms","IRF_Com","VIF_forms"))

#create dea data object with selected inputs and outputs - Model 3
dea_data3 <- read_data(d, dmus = 1, inputs = c("Station_Flow_Rank","Test_Scores","Staff.."), outputs = c("IRF_forms","IRF_Com","VIF_forms", "Average_VIF_com_INDV"))

#create dea data object with selected inputs and outputs - Model 4
dea_data4 <- read_data(d, dmus = 1, inputs = c("Station_Flow_Rank","Test_Scores","Staff..","Station_Duration"), outputs = c("IRF_forms","IRF_Com","VIF_forms", "Average.Min.Value"))

#create dea data object with selected inputs and outputs - Model 5
dea_data5 <- read_data(d, dmus = 1, inputs = c("Station_Flow_Rank","Test_Scores","Staff..","Station_Duration"), outputs = c("IRF_forms","IRF_Com","VIF_forms", "AVERAGE.using.Max"))
```


```{r}
#develop basic dea output oriented, variable returns-to-scale model
result <- model_basic(dea_data,orientation = "oo",rts = "vrs")

## since this is a output oriented need to take reciprocal to find relative efficiences
eff <- efficiencies(result) 
slack <- slacks(result)# To extract input and output slacks.
target <- targets(result)# To extract the input and output target values. 
lambda <- lambdas(result)# To extract the lambdas (or intensities). 
ref <- references(result)# To extract the reference set for inefficient DMUs. 
rts <- rts(result)# To extract the returns-to-scale. 
```

```{r}
#calculate relevant metrics
round(1 / eff,3)
#slack
#target
#lambda
#ref
#rts
#summary of dea model result
summary(result, exportExcel = F)
```

```{r}
#plot the efficiencies by station
plot(1/eff)

#plot the reference sets causing inefficient stations
plot(result)

```
Plots: 
1 - Bar chart showing the number of efficient & inefficient stations, as well as the relative level of inefficiency in the inefficient DMUs.
2 - Bar chart describing the number of appearances of the efficient DMUs in the inefficient DMU's reference set. 
3 - Network graph showing the efficiency and inefficiency of DMUs, as well as how they are connected. Green nodes depict the efficiency frontier, and the size of the green nodes (as well as arrows pointing to it) show the relative importance of that node in making the inefficient nodes inefficient. 


"Note
(1) We can obtain negative cross-efficiency in the input-oriented DEA model under variable returns
to scale. However, the same does not happen in the case of the output oriented VRS DEA model.
For this reason, the proposal of **Lim and Zhu (2015)** is implemented in deaR to calculate the input oriented cross-efficiency model under variable returns-to-scale.
(2) The multiplier model can have alternate optimal solutions (see note 1 in model_multiplier). So,
depending on the optimal weights selected we can obtain different cross-efficinecy scores."

```{r}
#create crosefficiency object for model 1
cross <- cross_efficiency(dea_data,
                          orientation = "oo",
                          rts = "vrs",
                          selfapp = TRUE,  
                          M2 = FALSE,
                          M3 = FALSE)
#print out results
#cross
m1_cross <- cross$Arbitrary$cross_eff 
#cross$Arbitrary$e
```


```{r}
#calculate the efficiency ranking by taking the average of the cross-efficiency values of each station
avg_eff <- colMeans(1/m1_cross)
avg_eff %>% as.data.frame() %>% rownames_to_column("Station") %>% rename(CrossEffScore1 = ".") %>% arrange(desc(CrossEffScore1)) ->avg_eff
```


```{r}
#plot rankings for model 1
g1 <- ggplot(avg_eff, aes(reorder(Station,CrossEffScore1),CrossEffScore1)) + geom_bar(stat="identity", fill="#77dd77")+ coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = CrossEffScore1 + -0.03, label = round(CrossEffScore1, 2))) +ggtitle("Ranked Average Station Efficiency - Model 1")
g1
```

```{r}
#calculate cross efficiency values for model 2
#calculate average cross-efficiency values rankings
#plot the rankingsfor model 2
cross2 <- cross_efficiency(dea_data2,
                          orientation = "oo",
                          rts = "vrs",
                          selfapp = TRUE,  
                          M2 = FALSE,
                          M3 = FALSE)

avg_eff2 <- colMeans(1/cross2$Arbitrary$cross_eff)
avg_eff2 %>% as.data.frame() %>% rownames_to_column("Station") %>% rename(CrossEffScore2 = ".") %>% arrange(desc(CrossEffScore2)) ->avg_eff2

g2 <- ggplot(avg_eff2, aes(reorder(Station,CrossEffScore2),CrossEffScore2)) + geom_bar(stat="identity", fill="#77dd77")+ coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = CrossEffScore2 + -0.03, label = round(CrossEffScore2, 2))) +ggtitle("Ranked Average Station Efficiency - Model 2")
g2
```

```{r}
#calculate cross efficiency values for model 3
#calculate average cross-efficiency values rankings
#plot the rankingsfor model 3
cross3 <- cross_efficiency(dea_data3,
                          orientation = "oo",
                          rts = "vrs",
                          selfapp = TRUE,  
                          M2 = FALSE,
                          M3 = FALSE)

avg_eff3 <- colMeans(1/cross3$Arbitrary$cross_eff)
avg_eff3 %>% as.data.frame() %>% rownames_to_column("Station") %>% rename(CrossEffScore3 = ".") %>% arrange(desc(CrossEffScore3)) ->avg_eff3

g3 <- ggplot(avg_eff3, aes(reorder(Station,CrossEffScore3),CrossEffScore3)) + geom_bar(stat="identity", fill="#77dd77")+ coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = CrossEffScore3 + -0.03, label = round(CrossEffScore3, 2))) +ggtitle("Ranked Average Station Efficiency - Model 3")
g3
```

```{r}
#calculate cross efficiency values for model 4
#calculate average cross-efficiency values rankings
#plot the rankingsfor model 4
cross4 <- cross_efficiency(dea_data4,
                          orientation = "oo",
                          rts = "vrs",
                          selfapp = TRUE,  
                          M2 = FALSE,
                          M3 = FALSE)

avg_eff4 <- colMeans(1/cross4$Arbitrary$cross_eff)
avg_eff4 %>% as.data.frame() %>% rownames_to_column("Station") %>% rename(CrossEffScore4 = ".") %>% arrange(desc(CrossEffScore4)) ->avg_eff4

g4 <- ggplot(avg_eff4, aes(reorder(Station,CrossEffScore4),CrossEffScore4)) + geom_bar(stat="identity", fill="#77dd77")+ coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = CrossEffScore4 + -0.03, label = round(CrossEffScore4, 2))) +ggtitle("Ranked Average Station Efficiency - Model 4")
g4
```

```{r}
#calculate cross efficiency values for model 5
#calculate average cross-efficiency values rankings
#plot the rankingsfor model 5
cross5 <- cross_efficiency(dea_data5,
                          orientation = "oo",
                          rts = "vrs",
                          selfapp = TRUE,  
                          M2 = FALSE,
                          M3 = FALSE)

avg_eff5 <- colMeans(1/cross5$Arbitrary$cross_eff)
avg_eff5 %>% as.data.frame() %>% rownames_to_column("Station") %>% rename(CrossEffScore5 = ".") %>% arrange(desc(CrossEffScore5)) ->avg_eff5

g5 <- ggplot(avg_eff5, aes(reorder(Station,CrossEffScore5),CrossEffScore5)) + geom_bar(stat="identity", fill="#77dd77")+ coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = CrossEffScore5 + -0.03, label = round(CrossEffScore5, 2))) +ggtitle("Ranked Average Station Efficiency - Model 5")
g5
```

```{r}
#library(gridExtra)
#grid.arrange(g1,g2,g3,g4,g5, nrow=3)
```

Now let's explore how each station changes with the different model parameters. Let's do this through a slope graph. Each station will have it's own line showing it's changes in values over the five models. 

```{r}
#join efficiency rankings together in order to visualize
a <- inner_join(avg_eff, avg_eff2, by = "Station") 
a <- inner_join(a, avg_eff3, by = "Station")
a <- inner_join(a, avg_eff4, by = "Station")
a <- inner_join(a, avg_eff5, by = "Station")
```

```{r}
#transpose data
b <- t(a) %>% as.data.frame()
#write.csv(a, "cross-eff12.csv")
#load csv
cross.eff <- read.csv("cross-eff12.csv")
```

```{r}
#prep data for graph
avg_eff %>% mutate(Model = 1) %>% rename(CrossEffScores=CrossEffScore1) %>% rowid_to_column("Ranking") -> c
avg_eff2 %>% mutate(Model = 2) %>% rename(CrossEffScores=CrossEffScore2) %>% rowid_to_column("Ranking") -> c2
avg_eff3 %>% mutate(Model = 3) %>% rename(CrossEffScores=CrossEffScore3) %>% rowid_to_column("Ranking") -> c3
avg_eff4 %>% mutate(Model = 4) %>% rename(CrossEffScores=CrossEffScore4) %>% rowid_to_column("Ranking") -> c4
avg_eff5 %>% mutate(Model = 5) %>% rename(CrossEffScores=CrossEffScore5) %>% rowid_to_column("Ranking") -> c5
```

```{r}
#bind rows
c.e.bind <- bind_rows(c, c2, c3, c4, c5)
```

```{r}
#Slope chart showing cross-efficiency across the 5 models
plot5 <- ggplot(data = c.e.bind, aes(x = Model, y = -Ranking, group = Station)) +
  geom_line(aes(color = Station, alpha = 1), size = 2) +
  geom_point(aes(color = Station, alpha = 1), size = 4) +
  geom_text(data = c.e.bind %>% filter(Model == "1"), 
                  aes(label = paste0(Station, " : ", Ranking)) , 
                  hjust = "left", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = -.45, 
                  direction = "y") +
  geom_text(data = c.e.bind %>% filter(Model == "5"), 
                  aes(label = paste0(Station, " : ", Ranking)) , 
                  hjust = "right", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = .5, 
                  direction = "y") +
  # move the x axis labels up top
  scale_x_discrete(position = "top") +
  theme_bw() +
  # Format tweaks
  # Remove the legend
  theme(legend.position = "none") +
  # Remove the panel border
  theme(panel.border= element_blank()) +
  # Remove just about everything from the y axis
  theme(axis.title.y = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.grid.minor.y = element_blank()) +
  # Remove a few things from the x axis and increase font size
  theme(axis.title.x     = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x.top      = element_text(size=12)) +
  # Remove x & y tick marks
  theme(axis.ticks       = element_blank()) +
  # Format title & subtitle
  theme(plot.title       = element_text(size=14, face = "bold", hjust = 0.5)) +
  theme(plot.subtitle    = element_text(hjust = 0.5)) +
  #  Labelling as desired
  labs(
    title = "Ranking by Station by Model"
  )
plot5
```

As we can see, many Stations declined in ranking while others improved.

```{r}
#rank station sby average cros efficiency score
c.e.bind %>% 
  group_by(Station) %>% 
  summarise(avg = mean(CrossEffScores)) %>%
  arrange(desc(avg)) -> ranked_stations
```

```{r}
#create bar graph of rankings
g.all <- ggplot(ranked_stations, aes(reorder(Station,avg),avg)) + geom_bar(stat="identity", fill="#77dd77")+ coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = avg + -0.03, label = round(avg, 2))) +ggtitle("Ranked Station Efficiency - Average of All Models")
g.all
```

```{r}
#write to csv to do excel formatting of quarters
#write.csv(c.e.bind, "c.e.bind.csv")
c.e.bind.F <- read.csv("c.e.bind.F.csv")
```

```{r}
#rank station sby average cros efficiency score
c.e.bind.F %>% 
  group_by(Quarter, Station) %>% 
  summarise(avg = mean(CrossEffScores)) %>%
  mutate(rank = rank(-avg, ties.method = "first")) -> ranked_stations2

```

```{r}
#average cross efficiency graph
g10 <- ggplot(ranked_stations2, aes(Quarter, avg))

#creat dot plot graph of station efficiency
g10 + geom_line(aes(color = Station), size=2) + geom_point(aes(shape=Station)) + ggtitle("Avg. Cross Efficiency Scores by Station by Quarter - All Models") + scale_x_discrete(name ="Quarter", limits=c("1","2","3","4","5","6","7","8")) + scale_y_continuous(name ="Avg. Cross Efficiency Score")
```

```{r}
#average cross efficiency graph
g11 <- ggplot(ranked_stations2, aes(Quarter, avg))

#creat dot plot graph of station efficiency
g11 + geom_point(aes(shape=Station, color = Station), size=5) + ggtitle("Avg. Cross Efficiency Scores by Station by Quarter - All Models") + scale_x_discrete(name ="Quarter", limits=c("1","2","3","4","5","6","7","8")) + scale_y_continuous(name ="Avg. Cross Efficiency Score")
```

```{r}
#Slope chart showing cross-efficiency across the 5 models
plot5 <- ggplot(data = ranked_stations2, aes(x = Quarter, y = -rank, group = Station)) +
  geom_line(aes(color = Station, alpha = 1), size = 2) +
  geom_point(aes(color = Station, alpha = 1), size = 4) +
  geom_text(data = ranked_stations2 %>% filter(Quarter == "1"), 
                  aes(label = paste0(Station, " : ", rank)) , 
                  hjust = "left", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = -.45, 
                  direction = "y") +
  geom_text(data = ranked_stations2 %>% filter(Quarter == "8"), 
                  aes(label = paste0(Station, " : ", rank)) , 
                  hjust = "right", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = .5, 
                  direction = "y") +
  # move the x axis labels up top
  scale_x_discrete(position = "top") +
  theme_bw() +
  # Format tweaks
  # Remove the legend
  theme(legend.position = "none") +
  # Remove the panel border
  theme(panel.border= element_blank()) +
  # Remove just about everything from the y axis
  theme(axis.title.y = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.grid.minor.y = element_blank()) +
  # Remove a few things from the x axis and increase font size
  theme(axis.title.x     = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x.top      = element_text(size=12)) +
  # Remove x & y tick marks
  theme(axis.ticks       = element_blank()) +
  # Format title & subtitle
  theme(plot.title       = element_text(size=14, face = "bold", hjust = 0.5)) +
  theme(plot.subtitle    = element_text(hjust = 0.5)) +
  #  Labelling as desired
  labs(
    title = "Ranking by Station by Quarter"
  )
plot5
```


```{r}
#load csv
f.data <- read.csv("DEA_Results_5Models.csv", header = T)
```

```{r}
#subset data and set up ggplot
f.data %>% select(Quarter, Station, Model1) %>% ggplot(aes(Quarter,Station, color=Model1, shape=Model1))-> g1
#set up ggplot 


#create dot plot graph of station efficiency
g1 + geom_point(size=7) + scale_shape_manual(values = c(19, 18)) +scale_color_manual(values=c("#7befb2","#f1a9a0")) + ggtitle("Station Efficiency Breakdown - Model 1") + scale_x_discrete(name ="Quarter", 
                    limits=c("1","2","3","4","5","6","7","8"))
```
```{r}
#subset data and set up ggplot
f.data %>% select(Quarter, Station, Model2) %>% ggplot(aes(Quarter,Station, color=Model2, shape=Model2))-> g2
#set up ggplot 


#creat dot plot graph of station efficiency
g2 + geom_point(size=7) + scale_shape_manual(values = c(19, 18)) +scale_color_manual(values=c("#7befb2","#f1a9a0")) + ggtitle("Station Efficiency Breakdown - Model 2") + scale_x_discrete(name ="Quarter", 
                    limits=c("1","2","3","4","5","6","7","8"))
```
```{r}
#subset data and set up ggplot
f.data %>% select(Quarter, Station, Model3) %>% ggplot(aes(Quarter,Station, color=Model3, shape=Model3))-> g3
#set up ggplot 


#create dot plot graph of station efficiency
g3 + geom_point(size=7) + scale_shape_manual(values = c(19, 18)) +scale_color_manual(values=c("#7befb2","#f1a9a0")) + ggtitle("Station Efficiency Breakdown - Model 3") + scale_x_discrete(name ="Quarter", 
                    limits=c("1","2","3","4","5","6","7","8"))
```

```{r}
#subset data and set up ggplot
f.data %>% select(Quarter, Station, Model4) %>% ggplot(aes(Quarter,Station, color=Model4, shape=Model4))-> g4
#set up ggplot 


#creat dot plot graph of station efficiency
g4 + geom_point(size=7) + scale_shape_manual(values = c(19, 18)) +scale_color_manual(values=c("#7befb2","#f1a9a0")) + ggtitle("Station Efficiency Breakdown - Model 4") + scale_x_discrete(name ="Quarter", 
                    limits=c("1","2","3","4","5","6","7","8"))
```

```{r}
#subset data and set up ggplot
f.data %>% select(Quarter, Station, Model5) %>% ggplot(aes(Quarter,Station, color=Model5, shape=Model5))-> g5
#set up ggplot 


#creat dot plot graph of station efficiency
g5 + geom_point(size=7) + scale_shape_manual(values = c(19, 18)) +scale_color_manual(values=c("#7befb2","#f1a9a0")) + ggtitle("Station Efficiency Breakdown - Model 5") + scale_x_discrete(name ="Quarter", 
                    limits=c("1","2","3","4","5","6","7","8"))
```

```{r}
#set up ggplot 
gfull <- ggplot(station_df, aes(Quarter,Station, color=Status, shape=Status))

#creat dot plot graph of station efficiency
gfull + geom_point(size=7) + scale_shape_manual(values = c(19, 15, 18)) +scale_color_manual(values=c("#7befb2", "#d5b8ff", "#f1a9a0")) + ggtitle("Station Efficiency Breakdown - All Models") + scale_x_discrete(name ="Quarter", limits=c("1","2","3","4","5","6","7","8"))
```

This plot is an easy way to visualize multiple discrete variables. Here we used classification (status of station in the 5 DEA runs) as well as Station Name. It is clear to see which stations have been deemed always efficient and which are always inefficient. 

**MODEL 3**


```{r}
#calculate cross efficiency values for model 3
#calculate average cross-efficiency values rankings
#plot the rankingsfor model 3
cross3 <- cross_efficiency(dea_data3,
                          orientation = "oo",
                          rts = "vrs",
                          selfapp = TRUE,  
                          M2 = FALSE,
                          M3 = FALSE)

avg_eff3 <- colMeans(1/cross3$Arbitrary$cross_eff)
avg_eff3 %>% as.data.frame() %>% rownames_to_column("Station") %>% rename(CrossEffScore3 = ".") %>% arrange(desc(CrossEffScore3)) ->avg_eff3

g3 <- ggplot(avg_eff3, aes(reorder(Station,CrossEffScore3),CrossEffScore3)) + geom_bar(stat="identity", fill="#77dd77")+ coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = CrossEffScore3 + -0.03, label = round(CrossEffScore3, 2))) +ggtitle("Ranked Average Station Efficiency")
g3
```

```{r}
#write.csv(avg_eff3 , "dea_data3.csv")
m3.rank <- read.csv("model3.ranking.csv")
```

```{r}
#create bar chart with station cross-efficiency rankings
g10 <- ggplot(m3.rank, aes(reorder(Station,CrossEffScore3),CrossEffScore3)) + geom_col(aes(fill = CrossEffScore3)) + scale_fill_gradient(low="#b4ecb4", high="#218321") + coord_flip() + labs(x="Station", y = "Average Efficiency") +  geom_text(aes(x = Station, y = CrossEffScore3 + -0.03, label = round(CrossEffScore3, 3))) +ggtitle("Average Station Cross-Efficiency") + theme(legend.position = "none")
g10
```


```{r}
#subset data and set up ggplot
f.data %>% select(Quarter, Station, Model3) %>% ggplot(aes(Quarter,Station, color=Model3, shape=Model3))-> g3
#set up ggplot 


#create dot plot graph of station efficiency
g3 + geom_point(size=7) + scale_shape_manual(values = c(19, 18)) +scale_color_manual(values=c("#7befb2","#f1a9a0")) + ggtitle("Station Efficiency Breakdown") + scale_x_discrete(name ="Quarter", 
                    limits=c("1","2","3","4","5","6","7","8")) + theme(legend.title = element_blank())
```

```{r}
#rank station from model 3
c.e.bind.F %>% 
  filter(Model == 3) %>%
  group_by(Quarter, Station) %>% 
  summarise(avg = mean(CrossEffScores)) %>%
  mutate(rank = rank(-avg, ties.method = "first")) -> ranked_stations.m3

```


```{r}
#Slope chart showing cross-efficiency across the 5 models
plot10 <- ggplot(data = ranked_stations.m3, aes(x = Quarter, y = -rank, group = Station)) +
  geom_line(aes(color = Station, alpha = 1), size = 2) +
  geom_point(aes(color = Station, alpha = 1), size = 4) +
  geom_text(data = ranked_stations.m3 %>% filter(Quarter == "1"), 
                  aes(label = paste0(Station, " : ", rank)) , 
                  hjust = "left", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = -.45, 
                  direction = "y") +
  geom_text(data = ranked_stations.m3 %>% filter(Quarter == "8"), 
                  aes(label = paste0(Station, " : ", rank)) , 
                  hjust = "right", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = .5, 
                  direction = "y") +
  # move the x axis labels up top
  scale_x_discrete(position = "top") +
  theme_bw() +
  # Format tweaks
  # Remove the legend
  theme(legend.position = "none") +
  # Remove the panel border
  theme(panel.border= element_blank()) +
  # Remove just about everything from the y axis
  theme(axis.title.y = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.grid.minor.y = element_blank()) +
  # Remove a few things from the x axis and increase font size
  theme(axis.title.x     = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x.top      = element_text(size=12)) +
  # Remove x & y tick marks
  theme(axis.ticks       = element_blank()) +
  # Format title & subtitle
  theme(plot.title       = element_text(size=14, face = "bold", hjust = 0.5)) +
  theme(plot.subtitle    = element_text(hjust = 0.5)) +
  #  Labelling as desired
  labs(
    title = "Ranking by Station by Quarter"
  )
plot10

```
```{r}
#install.packages("ggrepel")
library(ggrepel)
```


```{r}
ggplot(data = ranked_stations.m3, aes(x = Quarter, y = -rank, group = Station)) +
  geom_line(aes(color = Station, alpha = 1), size = 2) +
  geom_point(aes(color = Station, alpha = 1), size = 4) +
  geom_text_repel(data = ranked_stations.m3 %>% filter(Quarter == "1"), 
                  aes(label = paste0(Station)) , 
                  hjust = "left", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = -.45, 
                  direction = "y") +
  geom_text_repel(data = ranked_stations.m3 %>% filter(Quarter == "8"), 
                  aes(label = paste0(Station)) , 
                  hjust = "right", 
                  fontface = "bold", 
                  size = 4, 
                  nudge_x = .5, 
                  direction = "y") +
  # move the x axis labels up top
 scale_x_discrete(name ="Quarter", 
                    limits=c("1","2","3","4","5","6","7","8")) +
  theme_bw() +
  # Format tweaks
  # Remove the legend
  theme(legend.position = "none") +
  # Remove the panel border
  theme(panel.border     = element_blank()) +
  # Remove just about everything from the y axis
  theme(axis.title.y     = element_blank()) +
  theme(axis.text.y      = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.grid.minor.y = element_blank()) +
  # Remove a few things from the x axis and increase font size
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x.top      = element_text(size=12)) +
  # Remove x & y tick marks
  theme(axis.ticks       = element_blank()) +
  # Format title & subtitle
  theme(plot.title       = element_text(size=14, face = "bold", hjust = 0.5)) +
  theme(plot.subtitle    = element_text(hjust = 0.5)) +
  #  Labelling as desired
   labs(
    title = "Ranking by Station by Quarter"
  )
```

```{r}
#average cross efficiency graph
g10 <- ggplot(ranked_stations.m3, aes(Quarter, avg))

#creat dot plot graph of station efficiency
g10 + geom_line(aes(color = Station), size=2) + geom_point(aes(shape=Station)) + ggtitle("Cross Efficiency Scores by Station by Quarter") + scale_x_discrete(name ="Quarter", limits=c("1","2","3","4","5","6","7","8")) + scale_y_continuous(name ="Cross Efficiency Score")
```

```{r}
#average cross efficiency graph
g11 <- ggplot(ranked_stations.m3, aes(Station, avg))

#create dot plot graph of station efficiency
g11 + geom_boxplot(aes(color = Station)) + ggtitle("Cross Efficiency Scores Boxplot by Station for Q1-Q8") + scale_y_continuous(name ="Cross Efficiency Score")
```

```{r}
#average cross efficiency graph
g12 <- ggplot(ranked_stations.m3, aes(Station, avg))

#creat dot plot graph of station efficiency
g12 + geom_violin(aes(color = Station)) + ggtitle("Cross Efficiency Scores Distribution by Station for Q1-Q8") + scale_y_continuous(name ="Cross Efficiency Score")
```

```{r}
#average cross efficiency graph
g13 <- ggplot(ranked_stations.m3, aes(Station, avg))

#creat dot plot graph of station efficiency
g13 + geom_dotplot(aes(fill = Station), dotsize = 1.5, binaxis = "y",stackdir = "center") + ggtitle("Cross Efficiency Scores Distribution by Station for Q1-Q8") + scale_y_continuous(name ="Cross Efficiency Score")
```

```{r}
#average cross efficiency graph
g14 <- ggplot(ranked_stations.m3, aes(Station, avg))

#creat dot plot graph of station efficiency
g14 + geom_dotplot(aes(fill = Station), dotsize = 1.5, binaxis = "y",stackdir = "center") + ggtitle("Cross Efficiency Scores Distribution by Station for Q1-Q8") + scale_y_continuous(name ="Cross Efficiency Score") + geom_text_repel(label = ranked_stations.m3$Quarter)
```

```{r}
#install.packages("maps")
library(maps)
nepal_map <- map_data("world", region = "Nepal")
ggplot(nepal_map, aes(x = long, y = lat, group = group)) +
  geom_polygon(colour = "white")
```


```{r}
library(rgdal)
```

```{r}
nepal.adm3.shp <- readOGR(dsn="./NepalMaps/baselayers/NPL_adm", layer="NPL_adm3", stringsAsFactors = FALSE)
nepal.adm3.shp.df <- fortify(nepal.adm3.shp, region = "NAME_3")
```

```{r}
map <- ggplot(data = nepal.adm3.shp.df, aes(x = long, y = lat, group = group))
```

```{r}
np.cities <- data.frame(state = rep("Nepal", 6), city = c("Kakarvitta", 
    "Nepalgunj", "Bhairawa", "Lahan", "Biratnagar", "Bhadrapur"), lat = c(26.647547, 28.065956, 27.500478, 26.721022, 26.450756, 26.638697), lng = c(88.156116, 81.636996,  83.459141, 86.479882, 87.275398, 87.990889))

d <- data.frame(lat = c(26.647547, 28.065956, 27.500478, 26.721022, 26.450756, 26.638697), lng = c(88.156116, 81.636996,  83.459141, 86.479882, 87.275398, 87.990889))
```

```{r}
theme_bare <- theme(
  axis.line = element_blank(), 
  axis.text.x = element_blank(), 
  axis.text.y = element_blank(),
  axis.ticks = element_blank(), 
  axis.title.x = element_blank(), 
  axis.title.y = element_blank(),
  legend.text=element_text(size=7),
  legend.title=element_text(size=8),
  panel.background = element_blank(),
  panel.border = element_rect(colour = "gray", fill=NA, size=0.5)
)

map + 
  geom_polygon(fill = "#3B7AAD") + geom_path() + coord_fixed(1.3) + guides(fill = FALSE) +
  theme_bare 
```

```{r}
# getting the map
mapgilbert <- get_map(nepal, zoom = 6, maptype = "hybrid")

# plotting the map with some points on it
ggmap(mapgilbert) +
geom_point(aes(x = lng, y = lat, stroke = 1), colour="red", data = np.cities, size =2.5) + 
  geom_label_repel(
    aes(lng, lat, label = city),
    data=np.cities,
    size = 4, 
    box.padding = 0.2, point.padding = 0.3,
    segment.color = 'black') + theme_bare
```

